---
title: "Mini Data Analysis Milestone 2"
output: md_document 
---

*To complete this milestone, you can either edit [this `.rmd` file](https://raw.githubusercontent.com/UBC-STAT/stat545.stat.ubc.ca/master/content/mini-project/mini-project-2.Rmd) directly. Fill in the sections that are commented out with `<!--- start your work here--->`. When you are done, make sure to knit to an `.md` file by changing the output in the YAML header to `github_document`, before submitting a tagged release on canvas.*

# Welcome to the rest of your mini data analysis project!

In Milestone 1, you explored your data. and came up with research questions. This time, we will finish up our mini data analysis and obtain results for your data by: 

- Making summary tables and graphs 
- Manipulating special data types in R: factors and/or dates and times.
-   Fitting a model object to your data, and extract a result.
-   Reading and writing data as separate files.

We will also explore more in depth the concept of *tidy data.* 

**NOTE**: The main purpose of the mini data analysis is to integrate what you learn in class in an analysis. Although each milestone provides a framework for you to conduct your analysis, it's possible that you might find the instructions too rigid for your data set. If this is the case, you may deviate from the instructions -- just make sure you're demonstrating a wide range of tools and techniques taught in this class.

# Instructions

**To complete this milestone**, edit [this very `.Rmd` file](https://raw.githubusercontent.com/UBC-STAT/stat545.stat.ubc.ca/master/content/mini-project/mini-project-2.Rmd) directly. Fill in the sections that are tagged with `<!--- start your work here--->`.

**To submit this milestone**, make sure to knit this `.Rmd` file to an `.md` file by changing the YAML output settings from `output: html_document` to `output: github_document`. Commit and push all of your work to your mini-analysis GitHub repository, and tag a release on GitHub. Then, submit a link to your tagged release on canvas.

**Points**: This milestone is worth 50 points: 45 for your analysis, and 5 for overall reproducibility, cleanliness, and coherence of the Github submission. 

**Research Questions**: In Milestone 1, you chose two research questions to focus on. Wherever realistic, your work in this milestone should relate to these research questions whenever we ask for justification behind your work. In the case that some tasks in this milestone don't align well with one of your research questions, feel free to discuss your results in the context of a different research question.

# Learning Objectives

By the end of this milestone, you should:

-   Understand what *tidy* data is, and how to create it using `tidyr`.
-   Generate a reproducible and clear report using R Markdown.
-   Manipulating special data types in R: factors and/or dates and times.
-   Fitting a model object to your data, and extract a result.
-   Reading and writing data as separate files.

# Setup

Begin by loading your data and the tidyverse package below:

<<<<<<< HEAD

=======
>>>>>>> 9c5f7b898f7c2e6a4115ab037fef9b08c03b4a97
```{r, message = FALSE}
library(datateachr) # <- might contain the data you picked!
library(dplyr)
library(ggplot2)
library(tidyverse)
```


```{r}
library(here)
library(datateachr) 
library(dplyr)
library(ggplot2)
library(tidyverse)
```

# Task 1: Process and summarize your data 

From milestone 1, you should have an idea of the basic structure of your dataset (e.g. number of rows and columns, class types, etc.). Here, we will start investigating your data more in-depth using various data manipulation functions. 

### 1.1 (1 point) 

First, write out the 4 research questions you defined in milestone 1 were. This will guide your work through milestone 2:

<!-------------------------- Start your work below ---------------------------->
*1. What is the relationship between the age of the tree and plant area?* (This question used to be "What is the relationship between density of trees in a neighbourhood and the age of the trees planted?", however, upon further consideration, I did not believe there would be tangible correlation between density of tree clusters and age. Instead I wish to explore growth trends of trees based on species by first determining average diameter based on age.)

*2. What is the distribution of different species of “Spectacle” trees throughout Vancouver? (“Spectacle” trees is an subjective term that will be defined as species of that people visit as an attraction)*

*3. Which neighbourhood in Vancouver contain the most amounts of "Spectacle trees"?*
(This question used to be"Which streets in Vancouver have the most amount of trees with the largest plant area? Is there a relationship between plant area and how old a tree is?", however, upon further evaluation I believe this question to be distracted in scope. I wanted to narrow down the question in pursuit of finding the best places in Vancouver to view "Spectacle trees" in fall and spring respectively.

*4. What is the relationship between tree diameter and age of tree?*
(This question used to be " What is the relationship between species diversity and longitude/latitude? Is there a specific species that dominates a certain area of vancouver or is the distribution fairly equal?", however, upon further review this quesiton can be answered through my earlier inquiries so I wanted to gain more insight into growth patterns instead
<!----------------------------------------------------------------------------->

Here, we will investigate your data using various data manipulation and graphing functions.

### 1.2 (8 points)

Now, for each of your four research questions, choose one task from options 1-4 (summarizing), and one other task from 4-8 (graphing). You should have 2 tasks done for each research question (8 total). Make sure it makes sense to do them! (e.g. don't use a numerical variables for a task that needs a categorical variable.). Comment on why each task helps (or doesn't!) answer the corresponding research question.

Ensure that the output of each operation is printed!

Also make sure that you're using dplyr and ggplot2 rather than base R. Outside of this project, you may find that you prefer using base R functions for certain tasks, and that's just fine! But part of this project is for you to practice the tools we learned in class, which is dplyr and ggplot2.

**Summarizing:**

1.  Compute the *range*, *mean*, and *two other summary statistics* of **one numerical variable** across the groups of **one categorical variable** from your data.
2.  Compute the number of observations for at least one of your categorical variables. Do not use the function `table()`!
3.  Create a categorical variable with 3 or more groups from an existing numerical variable. You can use this new variable in the other tasks! *An example: age in years into "child, teen, adult, senior".*
4. Compute the proportion and counts in each category of one categorical variable across the groups of another categorical variable from your data. Do not use the function `table()`!

**Graphing:**

6. Create a graph of your choosing, make one of the axes logarithmic, and format the axes labels so that they are "pretty" or easier to read.
7. Make a graph where it makes sense to customize the alpha transparency.

Using variables and/or tables you made in one of the "Summarizing" tasks: 

8. Create a graph that has at least two geom layers. 
9. Create 3 histograms, with each histogram having different sized bins. Pick the "best" one and explain why it is the best.

Make sure it's clear what research question you are doing each operation for!

<!------------------------- Start your work below ----------------------------->

*What is the relationship between the age of the tree and the tree diameter?*

```{r}

# I am redefining my custom data set here because I had issues linking my first MDA file data set to this one. I hope this is okay :( 

vancouver_trees$Year_Column <- format(vancouver_trees$date_planted, "%Y") 

vancouver_trees_age <- vancouver_trees %>%
  mutate(Year_Column = as.numeric(format(date_planted, "%Y")),
         tree_age = 2023 - Year_Column) 

print(vancouver_trees_age)

```


1.  Compute the *range*, *mean*, and *two other summary statistics* of **one numerical variable** across the groups of **one categorical variable** from your data.

```{r}

vancouver_trees_age%>%
  filter(!is.na(tree_age)) %>%
  summarize(
    range_tree_age = max(tree_age) - min(tree_age),
    average_tree_age = mean(tree_age), 
    median_tree_age = median(tree_age), 
    sd_tree_age = sd(tree_age)
    )



```
8. Create a graph that has at least two geom layers. 


```{r}
library(ggplot2)

filtered_data <- na.omit(vancouver_trees_age[, c("plant_area", "tree_age", "diameter")])

# Create a scatterplot with a logarithmic y-axis (tree age)
ggplot(data = filtered_data, aes(x = plant_area, y = tree_age)) +
  geom_point(aes(size = diameter), alpha = 0.5, color = "darkgreen") +  # Add tree diameter as the size of points
  labs(
    title = "Relationship between Plant Area, Tree Age, and Diameter",
    x = "Plant Area",
    y = "Tree Age"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5))  # Rotate x-axis labels to be vertical

```

*What is the distribution of different species of “Spectacle” trees throughout Vancouver? (“Spectacle” trees is an subjective term that will be defined as species of that people visit as an attraction)*


2.  Compute the number of observations for at least one of your categorical variables. Do not use the function `table()`!

```{r}

species_count <- vancouver_trees_age %>%
  group_by(species_name) %>%
  summarise(Count = n())

# Print the result
print(species_count)

```
7. Make a graph where it makes sense to customize the alpha transparency.

```{r}
library(ggplot2)

filtered_data <- vancouver_trees_age %>%
  filter(genus_name %in% c("PRUNUS", "CORNUS", "ACER", "ABIES")) %>%
  na.omit()

ggplot(filtered_data, aes(x = longitude, y = latitude, fill = genus_name)) +
  geom_point(alpha = 1.0, shape = 21) +
  stat_density_2d(geom = "tile", contour = TRUE, alpha = 0.2) +
  scale_fill_manual(values = c("PRUNUS" = "pink", "CORNUS" = "hotpink", "ACER" = "orange", "ABIES" = "yellow")) +
  labs(
    title = "Distribution of Cherry Blossoms and Maple Trees in Vancouver",
    x = "Longitude",
    y = "Latitude"
  ) +
  theme_minimal()
```

Supplementary calculation to find Maple genus. We find that "ACER" and "ABIES" are out two genus' of interest. 

```{r}
search_string <- 'maple'

matching_rows <- grep(search_string, vancouver_trees_age$common_name, ignore.case = TRUE)

unique_values <- unique(vancouver_trees_age$common_name[matching_rows])

associated_values_list <- list()

for (val in unique_values) {
  associated_values_list[[val]] <- unique(vancouver_trees_age$genus_name[matching_rows[vancouver_trees_age$common_name[matching_rows] == val]])
}

result_trees <- data.frame(common_name = names(associated_values_list), genus_name = unlist(associated_values_list))

print(result_trees)
```

*Which neighbourhood in Vancouver contain the most amounts of "Spectacle trees"?*

2.  Compute the number of observations for at least one of your categorical variables. Do not use the function `table()`!

```{r}

library(dplyr)

spectacle_trees <- c("PRUNUS", "CORNUS", "ACER", "ABIES")

# Assuming 'vancouver_trees_age' is your dataset
tree_counts_by_genus_and_neighbourhood <- vancouver_trees_age %>%
  filter(genus_name %in% spectacle_trees) %>%  # Filter by selected genera
  group_by(neighbourhood_name, genus_name) %>%      # Group by street and genus
  summarize(tree_count = n()) %>%            # Count the number of trees in each group
  ungroup()

print(tree_counts_by_genus_and_neighbourhood)
```

8. Create a graph that has at least two geom layers. 


```{r}
#First I need to create a new function that tallies the amount of trees in each neighborhood

neighborhood_counts <- vancouver_trees_age %>%
  count(neighbourhood_name, name = "Total_Trees")

print(neighborhood_counts)
```


```{r}
# Create the bar plot with total trees on a log scale
plot <- ggplot(data = neighborhood_counts, aes(x = reorder(neighbourhood_name, -Total_Trees), y = Total_Trees)) +
  geom_bar(stat = "identity", fill = "darkgreen") +
  labs(
    title = "Number of Spectacle Trees in each Vancouver Neighborhood",
    x = "Neighbourhood",
    y = "Total Trees"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  coord_flip() +
  scale_y_log10()  # Apply log scale to the y-axis

# Calculate the average tree age for each neighborhood
average_age <- filtered_data %>%
  group_by(neighbourhood_name) %>%
  summarise(Average_Age = mean(tree_age, na.rm = TRUE))

# Add a line plot layer for the average tree age
plot + geom_line(data = average_age, aes(x = reorder(neighbourhood_name, -Average_Age), y = Average_Age, group = 1), color = "red") +
  labs(y = "Total Trees / Average Age (x10)")

```




*What is the relationship between tree diameter and age of tree?*

3.  Create a categorical variable with 3 or more groups from an existing numerical variable. You can use this new variable in the other tasks! *An example: age in years into "child, teen, adult, senior".*

```{r}


vancouver_trees_age$Diameter_string <- cut(vancouver_trees_age$diameter, 
                                               breaks = c(-Inf, 10, 20, 30, Inf), 
                                               labels = c("xsmall_width", "small_width", "medium_width", "large_width"),
                                               include.lowest = TRUE)


print(head(vancouver_trees_age$Diameter_string, 10))



```

7. Make a graph where it makes sense to customize the alpha transparency.


```{r}

library(ggplot2)

# Filter out rows with missing values in tree_age and diameter
filtered_data <- na.omit(vancouver_trees_age[, c("tree_age", "diameter", "Diameter_string")])

# Create a scatterplot with custom colors and alpha transparency
ggplot(data = filtered_data, aes(x = tree_age, y = diameter, color = Diameter_string)) +
  geom_point(aes(alpha = 0), size = 3) +
  labs(
    title = "Relationship between Tree Diameter and Age",
    x = "Tree Age",
    y = "Tree Diameter"
  ) +
  scale_color_manual(values = c("xsmall_width" = "red", "small_width" = "blue", "medium_width" = "green", "large_width" = "purple")) +
  scale_alpha(range = c(0.1, 1.0))  # Adjust the alpha range as needed




```



<!----------------------------------------------------------------------------->

### 1.3 (2 points)

Based on the operations that you've completed, how much closer are you to answering your research questions? Think about what aspects of your research questions remain unclear. Can your research questions be refined, now that you've investigated your data a bit more? Which research questions are yielding interesting results?

<!------------------------- Write your answer here ---------------------------->

*1. What is the relationship between the age of the tree and plant area?* 

With the graph associated with this question, I am much closer to answer the research question. I think to clarify the data further, I may need to insert a trend line to see if there is a actual correlation or relationship between age of a tree and plant area. I do not believe I needed a second geom layer showing diameter of trees to answer this specific question, but it gives greater context regarding my question 4 below. 

*2. What is the distribution of different species of “Spectacle” trees throughout Vancouver? (“Spectacle” trees is an subjective term that will be defined as species of that people visit as an attraction)*

Firstly, it was helpful to define the specific genus of trees that are defined as "spectacle trees". Being able to graph them based on longitude and latitude with color coding resulted in a very visual representation of spectacle trees. It seems that there are a lot more occurence of Maple than Cherry trees which matches my own knowledge regarding the distribution of these trees. I believe this research question was answered to the fullest extend and exceeded my own expectations in terms of results. 

*3. Which neighbourhood in Vancouver contain the most amounts of "Spectacle trees"?*

With the previously defined "spectacle trees" filter, it was a lot easier for me to graph the total amount of spectacle trees per neighbourhood. Although my initial inquiry is answered and I have found Dunbar-Southlands to contain the most amount of spectacle trees overall, I may try to insert a stacked bar chart in the future to visualize the distribution of genus amonst the existing tally of spectacle trees. 

*4. What is the relationship between tree diameter and age of tree?*

This relationship was a lot easier to find as the two numerical metrics were already predefined in my reformatted dataset. A curious finding for me was that on average, trees over 32 years of age had smaller diameters than those who are in the range of 19-29 years old. Presuming that tree trunks get thicker each year since another ring grows, this finding was quite surprising for me. 

<!----------------------------------------------------------------------------->

# Task 2: Tidy your data 

In this task, we will do several exercises to reshape our data. The goal here is to understand how to do this reshaping with the `tidyr` package.

A reminder of the definition of *tidy* data:

-   Each row is an **observation**
-   Each column is a **variable**
-   Each cell is a **value**

### 2.1 (2 points)

Based on the definition above, can you identify if your data is tidy or untidy? Go through all your columns, or if you have \>8 variables, just pick 8, and explain whether the data is untidy or tidy.

<!--------------------------- Start your work below --------------------------->

To answer this question, I will be analyzing whether my vancouver_trees_age dataset is clean or not. I will be showing data below from the first 8 columns.For the most part, the data is tidy as it follows the aforementioned three statements defining tidy data. Each column highlights a specific variable and does not additionally expand any column values. During the data cleaning process, I did not choose to ommit outliers that had missing values within a row. Specifically, "cultivar_name" column within the first 8 columns includes some NA values. I chose not to remove these rows because "cultivar_name" was not a column of data I was using in my analysis. Since the rest of the observations were complete, I decided that I could still include them in the dataset. 

```{r}
#Demonstration of first 8 columns

first_8_columns <- vancouver_trees_age[, 1:8]
print(first_8_columns)


```


<!----------------------------------------------------------------------------->

### 2.2 (4 points)

Now, if your data is tidy, untidy it! Then, tidy it back to it's original state.

If your data is untidy, then tidy it! Then, untidy it back to it's original state.

Be sure to explain your reasoning for this task. Show us the "before" and "after".

<!--------------------------- Start your work below --------------------------->

```{r}
#Since I previously categorized my data as tidy, I will first untidy the data by expanding the column "assigned".

wide_data <- pivot_wider(
  data = vancouver_trees_age,
  names_from = assigned,
  values_from = assigned
)

# Print the resulting dataset
print(wide_data)
```


```{r}

# The following formula makes my dataset tidy again

wide_data <- wide_data %>%
  mutate(assigned = coalesce(N, Y)) %>%
  select(-N, -Y)

# Print the resulting dataset
print(wide_data)

```




<!----------------------------------------------------------------------------->

### 2.3 (4 points)

Now, you should be more familiar with your data, and also have made progress in answering your research questions. Based on your interest, and your analyses, pick 2 of the 4 research questions to continue your analysis in the remaining tasks:

<!-------------------------- Start your work below ---------------------------->

1.  *Which neighbourhood in Vancouver contain the most amounts of "Spectacle trees"?*

2.  *What is the relationship between tree diameter and age of tree?*


<!----------------------------------------------------------------------------->

Explain your decision for choosing the above two research questions.

<!--------------------------- Start your work below --------------------------->

*For question 1:* I want to further explore the genus of spectacle trees in each neighbourhood. This can be done by aggregating a count of the trees of each genus in each neighbourhood, allowing me to superimpose the data on top of each other in a stacked bar chart. 

*For question 2:*Now that I can create a scatter plot for these two variables, I would like to add a linear model to see if I can extrapolate any trends for specific species types . 

<!----------------------------------------------------------------------------->

Now, try to choose a version of your data that you think will be appropriate to answer these 2 questions. Use between 4 and 8 functions that we've covered so far (i.e. by filtering, cleaning, tidy'ing, dropping irrelevant columns, etc.).

(If it makes more sense, then you can make/pick two versions of your data, one for each research question.) 

<!--------------------------- Start your work below --------------------------->

# Task 3: Modelling

## 3.0 (no points)

Pick a research question from 1.2, and pick a variable of interest (we'll call it "Y") that's relevant to the research question. Indicate these.

<!-------------------------- Start your work below ---------------------------->

**Research Question**: *What is the relationship between tree diameter and age of tree?*



**Variable of interest**: diameter

<!----------------------------------------------------------------------------->

## 3.1 (3 points)

Fit a model or run a hypothesis test that provides insight on this variable with respect to the research question. Store the model object as a variable, and print its output to screen. We'll omit having to justify your choice, because we don't expect you to know about model specifics in STAT 545.

-   **Note**: It's OK if you don't know how these models/tests work. Here are some examples of things you can do here, but the sky's the limit.

    -   You could fit a model that makes predictions on Y using another variable, by using the `lm()` function.
    -   You could test whether the mean of Y equals 0 using `t.test()`, or maybe the mean across two groups are different using `t.test()`, or maybe the mean across multiple groups are different using `anova()` (you may have to pivot your data for the latter two).
    -   You could use `lm()` to test for significance of regression coefficients.

<!-------------------------- Start your work below ---------------------------->

```{r}
print(head(vancouver_trees_age))
```

```{r}


# Load the ggplot2 package
library(ggplot2)

# Assuming your data frame is named "wide_data"
# Filter the data for the "Japanese Snowbell" in the "Common_name" column
filtered_data <- vancouver_trees_age[vancouver_trees_age$common_name == "JAPANESE SNOWBELL", ]

# Remove rows with missing values in tree_age or diameter

# Create a scatter plot with tree age on the x-axis and diameter on the y-axis
scatter_plot <- ggplot(data = filtered_data, aes(x = tree_age, y = diameter)) +
  geom_point() +
  labs(
    title = "Scatter Plot of Tree Age vs. Diameter for Japanese Snowbell",
    x = "Tree Age",
    y = "Diameter"
  ) +
  geom_smooth(method = "lm", se = FALSE, color = "blue") +  # Add a linear model line
  scale_x_log10() +  # Add log scale to x-axis
  scale_y_log10()    # Add log scale to y-axis

# Print the scatter plot
print(scatter_plot)



```



<!----------------------------------------------------------------------------->

## 3.2 (3 points)

Produce something relevant from your fitted model: either predictions on Y, or a single value like a regression coefficient or a p-value.

-   Be sure to indicate in writing what you chose to produce.
-   Your code should either output a tibble (in which case you should indicate the column that contains the thing you're looking for), or the thing you're looking for itself.
-   Obtain your results using the `broom` package if possible. If your model is not compatible with the broom function you're needing, then you can obtain your results by some other means, but first indicate which broom function is not compatible.

<!-------------------------- Start your work below ---------------------------->

I am looking to find multiple regression coefficients such as the estimated coefficients for the linear regression model, the standard error, the statistic and the p.value. I am hoping by gathering these 4 metrics that I will get a better understanding of the relationship between tree age and tree diameter. 

```{r}
# Load the necessary packages
library(ggplot2)
library(broom)

filtered_data <- vancouver_trees_age[vancouver_trees_age$common_name == "JAPANESE SNOWBELL", ]

# Fit a linear model to the data
lm_model <- lm(diameter ~ tree_age, data = filtered_data)

# Extract the regression coefficients using broom
coefficients_df <- tidy(lm_model)

# Print the coefficients
print(coefficients_df)

```


<!----------------------------------------------------------------------------->

# Task 4: Reading and writing data

Get set up for this exercise by making a folder called `output` in the top level of your project folder / repository. You'll be saving things there.

## 4.1 (3 points)

Take a summary table that you made from Task 1, and write it as a csv file in your `output` folder. Use the `here::here()` function.

-   **Robustness criteria**: You should be able to move your Mini Project repository / project folder to some other location on your computer, or move this very Rmd file to another location within your project repository / folder, and your code should still work.
-   **Reproducibility criteria**: You should be able to delete the csv file, and remake it simply by knitting this Rmd file.

<!-------------------------- Start your work below ---------------------------->

First I will create a new "output" folder for my work. 
```{r}
# Define the folder name
output_folder <- "output"

# Check if the folder already exists; if not, create it
if (!dir.exists(output_folder)) {
  dir.create(output_folder)
} else {
  cat(paste("The folder", output_folder, "already exists.\n"))
}

# Set the working directory to the "output" folder
setwd(output_folder)

```
I have selected to use the following research question for this assignment: 
*What is the distribution of different species of “Spectacle” trees throughout Vancouver? (“Spectacle” trees is an subjective term that will be defined as species of that people visit as an attraction)*

2.  Compute the number of observations for at least one of your categorical variables. Do not use the function `table()`!

```{r}

# Summarize the data
species_count <- vancouver_trees_age %>%
  group_by(species_name) %>%
  summarise(Count = n())

# Specify the output file path using here::here()
output_file <- here::here("output", "species_summary.csv")

# Save the summary table as a CSV file
write.csv(species_count, output_file, row.names = FALSE)

# Confirm the file has been created
cat("CSV file saved:", output_file, "\n")


```



<!----------------------------------------------------------------------------->

## 4.2 (3 points)

Write your model object from Task 3 to an R binary file (an RDS), and load it again. Be sure to save the binary file in your `output` folder. Use the functions `saveRDS()` and `readRDS()`.

-   The same robustness and reproducibility criteria as in 4.1 apply here.

<!-------------------------- Start your work below ---------------------------->
For reference, here is the code again for my model in Task 3: 
```{r}

# Load the ggplot2 package
library(ggplot2)

# Assuming your data frame is named "wide_data"
# Filter the data for the "Japanese Snowbell" in the "Common_name" column
filtered_data <- vancouver_trees_age[vancouver_trees_age$common_name == "JAPANESE SNOWBELL", ]

# Remove rows with missing values in tree_age or diameter

# Create a scatter plot with tree age on the x-axis and diameter on the y-axis
scatter_plot <- ggplot(data = filtered_data, aes(x = tree_age, y = diameter)) +
  geom_point() +
  labs(
    title = "Scatter Plot of Tree Age vs. Diameter for Japanese Snowbell",
    x = "Tree Age",
    y = "Diameter"
  ) +
  geom_smooth(method = "lm", se = FALSE, color = "blue") +  # Add a linear model line
  scale_x_log10() +  # Add log scale to x-axis
  scale_y_log10()    # Add log scale to y-axis

# Print the scatter plot
print(scatter_plot)


```

```{r}
# Your code to create the model object
# ...

# Save the model object to an RDS file
model_regression <- here::here("output", "your_model.rds")
saveRDS(scatter_plot, file = model_regression)

# Load the model object from the RDS file
loaded_model <- readRDS(model_regression)

# You can now use the loaded_model object
# ...

```


<!----------------------------------------------------------------------------->

# Overall Reproducibility/Cleanliness/Coherence Checklist 

Here are the criteria we're looking for.

## Coherence (0.5 points)

The document should read sensibly from top to bottom, with no major continuity errors. 

The README file should still satisfy the criteria from the last milestone, i.e. it has been updated to match the changes to the repository made in this milestone. 

## File and folder structure (1 points)

You should have at least three folders in the top level of your repository: one for each milestone, and one output folder. If there are any other folders, these are explained in the main README.

Each milestone document is contained in its respective folder, and nowhere else.

Every level-1 folder (that is, the ones stored in the top level, like "Milestone1" and "output") has a `README` file, explaining in a sentence or two what is in the folder, in plain language (it's enough to say something like "This folder contains the source for Milestone 1").

## Output (1 point)

All output is recent and relevant:

-   All Rmd files have been `knit`ted to their output md files. 
-   All knitted md files are viewable without errors on Github. Examples of errors: Missing plots, "Sorry about that, but we can't show files that are this big right now" messages, error messages from broken R code
-   All of these output files are up-to-date -- that is, they haven't fallen behind after the source (Rmd) files have been updated.
-   There should be no relic output files. For example, if you were knitting an Rmd to html, but then changed the output to be only a markdown file, then the html file is a relic and should be deleted.

Our recommendation: delete all output files, and re-knit each milestone's Rmd file, so that everything is up to date and relevant.

## Tagged release (0.5 point)

You've tagged a release for Milestone 2. 

### Attribution

Thanks to Victor Yuan for mostly putting this together.
